Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-11-15 manuscript.tex
stack faster than recursion is not a result
Make it clear that the stack vs recursion speed claim is not based on
experimental results but as a rule of thumb

This stack-based implementation
has some advantages over the original recursive implementation,
namely:
(1) It will be faster because it bypasses the overhead of function calls.
(2) It gives the developer more control over the recursion step.
In recursive implementations,
the developer has no control over
the maximum number of consecutive recursive calls
(i.e., the ``recursion depth'').
This limit may vary with programming language,
compiler, and operating system.
Overflowing the maximum recursion depth
may result in program crashes,
typically with cryptic or inexistent error messages.
In the stack-based implementation,
the developer has complete control.
Overflowing of the stack can be handled gracefully
with an error message
or even performing a suitable approximation of the result.

@@

We have implemented and improved upon an adaptive discretization algorithm to
achieve an optimal division of tesseroids.
Tesseroids are divided into more parts closer to the computation point,
where more point masses are needed.
Our implementation of the adaptive discretization uses a ``stack'' data
structure in place of the originally proposed recursive implementation.
The stack-based algorithm is computationally faster and allows more control
over errors when too many divisions are necessary.
The adaptive discretization is controlled by
a scalar called the distance-size ratio ($D$).
The algorithm ensures that all tesseroids will
have dimensions smaller than $D$ times the distance to the computation point.
The value of $D$ indirectly controls the accuracy of the integration as well as
the computation time.

>>>>

This stack-based implementation
has some advantages over the original recursive implementation,
namely:
(1) It gives the developer more control over the recursion step.
(2) In general, it is faster because it bypasses the overhead of function
calls.
In recursive implementations,
the developer has no control over
the maximum number of consecutive recursive calls
(i.e., the ``recursion depth'').
This limit may vary with programming language,
compiler, and operating system.
Overflowing the maximum recursion depth
may result in program crashes,
typically with cryptic or inexistent error messages.
In the stack-based implementation,
the developer has complete control.
Overflowing of the stack can be handled gracefully
with an error message
or even performing a suitable approximation of the result.

@@

We have implemented and improved upon an adaptive discretization algorithm to
achieve an optimal division of tesseroids.
Tesseroids are divided into more parts closer to the computation point,
where more point masses are needed.
Our implementation of the adaptive discretization uses a ``stack'' data
structure in place of the originally proposed recursive implementation.
As a rule of thumb in procedural languages (like C),
stack-base implementations are computationally faster
than the equivalent code using function recursion.
Furthermore, the stack-based algorithm allows more control
over errors when too many divisions are necessary.
The adaptive discretization is controlled by
a scalar called the distance-size ratio ($D$).
The algorithm ensures that all tesseroids will
have dimensions smaller than $D$ times the distance to the computation point.
The value of $D$ indirectly controls the accuracy of the integration as well as
the computation time.
